---
title: "Peer-graded Assignment:R Markdown and Leaflet"
date: "5/15/2020"
output: 
html_document:
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Data 

The dataset used for this project is [COVID-19 Dataset](https://www.kaggle.com/imdevskp/corona-virus-report) rovided by Johns Hopkins University Center for Systems Science and Engineering (JHU CSSE), [full details](https://github.com/CSSEGISandData/COVID-19). The dataset contains number of Confirmed, Death and Recovered cases every day across the globe from 1/22/2020 to 5/14/2020.

```{r}
df <- read.csv("covid_19.csv")
head(df)
```

The data is grouped by Country, Latitude, and Longitude, then summerized by calculating least Confirmed, Deaths, and Recovered cases per country.

```{r}
library(dplyr)
df2 <- df %>% 
    group_by(Country.Region, Lat, Long) %>% 
    summarize(cases = max(Confirmed, na.rm = TRUE), 
              deaths = max(Deaths, na.rm = TRUE), 
              recovered = max(Recovered, na.rm = TRUE))
df2 <- df2 %>% rename(lat = Lat, lng = Long)
    
```


## Coronavirus (COVID-19) map

The map shows number of confirmed, recoverd, and death cases in each country when Circles are clicked.

```{r}
library(leaflet)
df2 %>%
    leaflet() %>%
    addTiles() %>%
    addCircles(weight = 1, radius = df2$cases * 2,
               popup = paste("Country:",  df2$Country.Region, "<br>",
                             "Confirmed:",  df2$cases, "<br>",
                             "Recovered:", df2$recovered, "<br>",
                             "Deaths:", df2$deaths, "<br>"))
```












